---
title: 'Assignment 2: Data Collection and Text Mining'
author: "Kevin Frew (20742541) & Nicole Rothwell (21970548)"
date: "02/07/2021"
output: html_document
---
##Set up of the general environment:
```{r}
#pacman installs a package before loading it if it is not already installed
if (!require("pacman")) install.packages("pacman"); 
library(pacman)
pacman::p_load(tidyverse, dplyr, rtweet)
```
###Get the most recent 3,200 tweets from Mia Malan, News24, HealthZA and SABC News
```{r}
## get user IDs of accounts 
tweets <- get_timelines(c("miamalan", "News24", "HealthZA", "SABCNews"), n = 3200)

```
###Write the tweets to a csv file called 'twitter'
```{r}
write_as_csv(tweets, "twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

save_as_csv(tweets, "twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
```

###1.1 Get the most recent tweets from Mia Malan
```{r}
## get user IDs of accounts 
miamalan_tweets <- get_timelines(c("miamalan"), n = 3200)
```
###Write the tweets to a csv file called 'malan_twitter'
```{r}
write_as_csv(miamalan_tweets, "malan_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

save_as_csv(miamalan_tweets, "malan_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
```

###1.2 Get the most recent tweets from News24
```{r}
## get user IDs of accounts 
news_tweets <- get_timelines(c("News24"), n = 3200)
```
###Write the tweets to a csv file called 'news_twitter'
```{r}
write_as_csv(news_tweets, "news_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

save_as_csv(news_tweets, "news_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
```

###1.3 Get the most recent tweets from HealthZA
```{r}
## get user IDs of accounts 
government_tweets <- get_timelines(c("HealthZA"), n = 3200)
```
###Write the tweets to a csv file called 'government_twitter'
```{r}
write_as_csv(government_tweets, "government_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

save_as_csv(government_tweets, "government_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
```

###1.4 Get the most recent tweets from SABCNews
```{r}
## get user IDs of accounts
sabc_tweets <- get_timelines(c("SABCNews"), n = 3200)
```
###Write the tweets to a csv file called 'sabc_twitter'
```{r}
write_as_csv(sabc_tweets, "sabc_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")

save_as_csv(sabc_tweets, "sabc_twitter.csv", prepend_ids = TRUE, na = "", fileEncoding = "UTF-8")
```
















